---
title: "Problem2"
author: "MDS202203"
date: "2022-11-15"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 2 : Simulation Study to Understand Sampling Distribution

**Part A** Suppose $X_1,X_2,\cdots,X_n\stackrel{iid}{\sim} Gamma(\alpha,\sigma)$, with pdf as $$
f(x | \alpha,\sigma)=\frac{1}{\sigma^{\alpha}\Gamma(\alpha)}e^{- x/\sigma}x^{\alpha-1},~~~~0<x<\infty,
$$ 1. Write a `function` in `R` which will compute the MLE of $\theta=\log(\alpha)$ using `optim` function in `R`. You can name it `MyMLE` 2. Choose `n=20`, and `alpha=1.5` and `sigma=2.2` (i) Simulate $\{X_1,X_2,\cdots,X_n\}$ from `rgamma(n=20,shape=1.5,scale=2.2)` (ii) Apply the `MyMLE` to estimate $\theta$ and append the value in a vector (iii) Repeat the step (i) and (ii) 1000 times (iv) Draw histogram of the estimated MLEs of $\theta$. (v) Draw a vertical line using `abline` function at the true value of $\theta$. (vi) Use `quantile` function on estimated $\theta$'s to find the 2.5 and 97.5-percentile points. 3. Choose `n=40`, and `alpha=1.5` and repeat the (2). 4. Choose `n=100`, and `alpha=1.5` and repeat the (2). 5. Check if the gap between 2.5 and 97.5-percentile points are shrinking as sample size `n` is increasing?

*Hint*: Perhaps you should think of writing a single `function` where you will provide the values of `n`, `sim_size`, `alpha` and `sigma`; and it will return the desired output.

```{r}
our_function= function(n, sim_size,alpha1, sigma1){
  mle=c()
  for(i in 1:sim_size){
    X = rgamma(n,alpha1,scale= sigma1)
    total=sum(log(X))
    sigma2= var(X)/mean(X)
    alpha2=mean(X)^2/var(X)
    n= length(X)
    MyMLE=function(parametes){
    alpha= parametes[1]
    sigma= parametes[2]
    log_likli= -n*alpha*log(sigma)-n*log(gamma(alpha))-sum(X)/sigma +(alpha-1)*total
    return(-log_likli)
    }
    fit= optim(c(alpha2,sigma2), MyMLE)
    mle=append(mle,log(fit$par[1]))
  }
  hist(mle, breaks=50)
  abline(v=log(alpha1))
  ml= data.frame(mle)
  quantile(ml, na.rm= T, probs= c(0.025,0.975))

} 
print(our_function(20,1000,1.5,2.2))
print(our_function(40,1000,1.5,2.2))
print(our_function(100,1000,1.5,2.2))

```

As we increase the sample size we observe that distance between 2.5 percentile and 97.5 percentile decreases.
